Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-01-30 Paper.tex

The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_u$, the set of logs created through execution of the transaction, $R_\mathbf{l}$ and the Bloom filter composed from information in those logs, $R_b$ and the status code of the transaction, $R_z$:
\begin{equation}
R \equiv (R_z, R_u, R_b, R_\mathbf{l})
\end{equation}

@@

0x56 & {\small JUMP} & 1 & 0 & Alter the program counter. \\

@@

@@

0x57 & {\small JUMPI} & 2 & 0 & Conditionally alter the program counter. \\

>>>>

\linkdest{transaction_receipt_R}{}\linkdest{tx_receipt_gas_used_R__u}{}The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_u$, the set of logs created through execution of the transaction, $R_\mathbf{l}$ and the Bloom filter composed from information in those logs, $R_b$ and the status code of the transaction, $R_z$:

\begin{equation}
R \equiv (R_z, R_u, R_b, R_\mathbf{l})
\end{equation}

@@

\linkdest{JUMP}{}0x56 & {\small JUMP} & 1 & 0 & Alter the program counter. \\

@@

&&&& This has the effect of writing said value to $\boldsymbol{\mu}_{pc}$. See section \ref{ch:model}.\\

@@

\linkdest{JUMPI}{}0x57 & {\small JUMPI} & 2 & 0 & Conditionally alter the program counter. \\
